### 2021-11-12 documents/floats/hixintro.tex
many changes and additions to introduction

\begin{table}
\centering
\caption[Some \hixka verbs]{Some \hixka verbs \parencites[150, 510, 511, 513]{howard2001wrought}[27, 69, 70]{hixkaryanaderby1985}}
\label{tab:hixintro}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &     \qu{to fall} &  \qu{to be afraid} &          \qu{to walk} &    \qu{to go} \\
\midrule
\gl{1}   &  \obj{k-ehurka-} &  \obj{k-oserʲehɨ-} &  \obj{k-atarʲeknohɨ-} &   \obj{ɨ-to-} \\
\gl{2}   &  \obj{m-ehurka-} &  \obj{m-oserʲehɨ-} &  \obj{m-atarʲeknohɨ-} &  \obj{mɨ-to-} \\
\gl{1+2} &  \obj{t-ehurka-} &  \obj{t-oserʲehɨ-} &  \obj{t-atarʲeknohɨ-} &  \obj{tɨ-to-} \\
\gl{3}   &  \obj{ɲ-ehurka-} &  \obj{n-oserʲehɨ-} &  \obj{n-atarʲeknohɨ-} &   \obj{n-to-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Some \hixka verbs]{Some \hixka verbs \parencites[150, 510, 511, 513, 520]{howard2001wrought}[197, 198]{hixkaryanaderby1985}}
\label{tab:hixintro}
\begin{tabular}[t]{@{}llllll@{}}
\mytoprule
{} &     \qu{to fall} &  \qu{to be afraid} &          \qu{to walk} & \qu{to cut self} &    \qu{to be} \\
\midrule
\gl{1}   &  \obj{k-ehurka-} &  \obj{k-oserʲehɨ-} &  \obj{k-atarʲeknohɨ-} &   \obj{k-atama-} &  \obj{w-eʃe-} \\
\gl{2}   &  \obj{m-ehurka-} &  \obj{m-oserʲehɨ-} &  \obj{m-atarʲeknohɨ-} &   \obj{m-atama-} &  \obj{m-eʃe-} \\
\gl{1+2} &  \obj{t-ehurka-} &  \obj{t-oserʲehɨ-} &  \obj{t-atarʲeknohɨ-} &   \obj{t-atama-} &  \obj{t-eʃe-} \\
\gl{3}   &  \obj{ɲ-ehurka-} &  \obj{n-oserʲehɨ-} &  \obj{n-atarʲeknohɨ-} &   \obj{n-atama-} &  \obj{n-eʃe-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-11-12 documents/floats/triintro.tex
many changes and additions to introduction

\begin{table}
\centering
\caption[Some \trio verbs]{Some \trio verbs \parencites[292, 294]{triomeira1999}}
\label{tab:triintro}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &      \qu{to sleep} & \qu{to bathe (\gl{intr})} &     \qu{to yawn} &    \qu{to say} \\
\midrule
\gl{1}   &    \obj{t-əənɨkɨ-} &              \obj{s-epɨ-} &  \obj{s-entapo-} &   \obj{wɨ-ka-} \\
\gl{2}   &    \obj{m-əənɨkɨ-} &              \obj{m-epɨ-} &  \obj{m-entapo-} &   \obj{mɨ-ka-} \\
\gl{1+2} &  \obj{kɨt-əənɨkɨ-} &             \obj{ke-epɨ-} &  \obj{k-entapo-} &  \obj{kɨh-ka-} \\
\gl{3}   &    \obj{n-əənɨkɨ-} &              \obj{n-epɨ-} &  \obj{n-entapo-} &    \obj{n-ka-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Some \trio verbs]{Some \trio verbs \parencites[292, 294]{triomeira1999}[274]{triocarlin2004}}
\label{tab:triintro}
\begin{tabular}[t]{@{}llllll@{}}
\mytoprule
{} &      \qu{to sleep} & \qu{to see self} & \qu{to bathe (\gl{intr})} &     \qu{to yawn} &     \qu{to go} \\
\midrule
\gl{1}   &    \obj{t-əənɨkɨ-} &    \obj{t-əene-} &              \obj{s-epɨ-} &  \obj{s-entapo-} &  \obj{wɨ-tən-} \\
\gl{2}   &    \obj{m-əənɨkɨ-} &    \obj{m-əene-} &              \obj{m-epɨ-} &  \obj{m-entapo-} &  \obj{mɨ-tən-} \\
\gl{1+2} &  \obj{kɨt-əənɨkɨ-} &    \obj{k-əene-} &             \obj{ke-epɨ-} &  \obj{k-entapo-} &  \obj{kɨ-tən-} \\
\gl{3}   &    \obj{n-əənɨkɨ-} &    \obj{n-əene-} &              \obj{n-epɨ-} &  \obj{n-entapo-} &  \obj{nɨ-tən-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-11-12 documents/sections/extensions.tex
discussion and factor comparison
many changes and additions to introduction

\subsection{\PPek \rc{k-}}
\label{sec:pekodian}
The Pekodian branch was suggested by \textcite{meira2005southern}, as the result of fieldwork on \bakairi by Meira and the availability of more material on \ikpeng. % \parencites{pacheco1997relativizacao}{ikpengpacheco1997}{campetela1997analise}{pacheco1998nominalizacao}{ikpengpacheco2001}{campetela2002aspectos}{pacheco2002aspectos}{pacheco2003intransitivos}.
It consists of closely related \arara and \ikpeng, with \bakairi as a more distant member.
\textcite{meira2005southern} focused on phonological and lexical properties, so no reconstructive work on \PPek morphosyntax can be found in the literature.
All three Pekodian languages have a regular \gl{1}\gl{s_a_} marker \obj{k-}, as evidenced by the paradigms in \cref{tab:pekreg}.\footnote{In \cref{tab:pekreg} and the remainder of this paper, we omit any possible TAM suffixes from the attested forms in the literature, since a) our focus lies on the prefixes and stems, and b) full paradigms containing the same TAM suffix are rarely found.}
We can thus reconstruct a \PPek \gl{1}\gl{s_a_} marker \rc{k-}.

@@

\ex<ikp-170>\ikpeng \parencite[][80]{ikpengpacheco2001}\\
\begingl
\gla k-aran-t͡ʃi//
\glb \gl{1}-go-\gl{npst}//
\glft \qu{I'm going.}//
\endgl
\xe
%
%\ex<ikp-182>\ikpeng \parencite[][320]{chagas2019ikpeng}\\
%\begingl
%\gla ∅-iptoŋ-lan//
%\glb \gl{3}\gl{s_a_}-sit.down-\gl{pst}//
%\glft \qu{She sat down.}//
%\endgl
%\xe
%

%\ex<ikpwloss> %\arara-\ikpeng \obj{w}:Ø correspondences\\
%\begin{tabular}[t]{@{}lll@{}}
%\PXin & \arara & \ikpeng\\
%\rc{wɨna} \qu{\gl{dat}} & \obj{wɨna} & \obj{ɨna}\\
%\rc{wokori} \qu{dog, jaguar} & \obj{wokori} & \obj{akari}\\
%\rc{tawe} \qu{capuchin monkey} & \obj{tawe} & \obj{tae}\\
%\rc{watke} \qu{to defecate} & \obj{watke} & \obj{atke}\\
%\rc{wɨnkɨ} \qu{to sleep} & \obj{wɨnkɨ} & \obj{ɨnkɨ}\\
%& (\obj{o-wɨnkɨ} \qu{sleep!}) & (\obj{j-ɨnkɨ-lɨ} \qu{s/he slept})\\
%\end{tabular}\\
%\parencites[80]{alves2017arara}[164, 67, 150]{ikpengpacheco2001}[9]{desouza2010arara}[68]{souza1993arara}[91]{alves2013verbo}[40]{campetela1997analise} 
%\xe

@@

%\ex<tri-130> \trio \parencite[][114]{triomeira1999}\\
%\begingl
%\gla n-epɨ//
%\glb \gl{3}-come//
%\glft \qu{S/he came.}//
%\endgl
%\xe

@@

%\pex<car1p>\carijo \parencite[][59, 53]{guerrero2016carijo}
%\begin{multicols}{2}
%\a<car-1>
%\begingl
%\gla jɨ-hɨnəh-ɨ//
%\glb \gl{3}>\gl{1}-kill-\gl{pfv}//
%\glft \qu{S/he killed me.}//
%\endgl
%\a<car-31>
%\begingl
%\gla j-owo-rɨ//
%\glb \gl{1}\gl{poss}-uncle-\gl{pert}//
%\glft \qu{my uncle}//
%\endgl
%\end{multicols}
%\xe
%

@@

%
%Interestingly enough, the verb \qu{to be} only shows \obj{w-} in its \obj{a} root allomorph, but not in the \obj{et͡ʃi} root allomorph, where it has \obj{j-} \exref{car1y.mivida-12}.
%In a somewhat foreshadowing move, I will note that \PTar \rc{(ət)epɨ} \qu{to come} was also affected by the \carijo extension, as seen in \exref{car1y.car-18}.
%As discussed in \cref{sec:taranoan}, this verb preserves \rc{w-} in \akuriyo and \trio \exref{tri-105}.
%
%\pex<car1y>\carijo
%\a<mivida-12>
%\begingl
%\glpreamble iretibə et͡ʃinəme gərə jet͡ʃiɨ//
%\gla ireti-bə et͡ʃi-nə=me gərə j-et͡ʃi-ɨ//
%\glb then-from be-\gl{inf}=\gl{attrz} still \gl{1}-be-\gl{pfv}//
%\glft \qu{Then I was already grown up.} \parencite[][177]{robayo1989rame}//
%\endgl
%\a<car-18>
%\begingl
%\gla əji-wa-e j-eh-ɨ//
%\glb \gl{2}-search-\gl{sup} \gl{1}-come-\gl{pfv}//
%\glft \qu{I came looking for you.} \parencite[][102]{guerrero2019carijo}//
%\endgl
%\xe
%
%\ex<tri-105>\trio \parencite[][337]{triocarlin2004}\\
%\begingl
%\gla ene w-əe//
%\glb see.\gl{sup} \gl{1}\gl{s_a_}-come//
%\glft \qu{I came to see him/her.}//
%\endgl
%\xe

>>>>

\subsection{\PPek \rc{k-}}
\label{sec:pekodian}
The Pekodian branch was suggested by \textcite{meira2005southern}, as the result of fieldwork on \bakairi by Meira and the availability of more material on \ikpeng. % \parencites{pacheco1997relativizacao}{ikpengpacheco1997}{campetela1997analise}{pacheco1998nominalizacao}{ikpengpacheco2001}{campetela2002aspectos}{pacheco2002aspectos}{pacheco2003intransitivos}.
It consists of closely related \arara and \ikpeng, with \bakairi as a more distant member.
\textcite{meira2005southern} focused on phonological and lexical properties, so no reconstructive work on \PPek morphosyntax can be found in the literature.
All three Pekodian languages have a regular \gl{1}\gl{s_a_} marker \obj{k-}, as evidenced by the paradigms in \cref{tab:pekreg}.
We can thus reconstruct a \PPek \gl{1}\gl{s_a_} marker \rc{k-}.

@@

\ex<ikp-170>\ikpeng \parencite[][80]{ikpengpacheco2001}\\
\begingl
\gla k-aran-t͡ʃi//
\glb \gl{1}-go-\gl{npst}//
\glft \qu{I'm going.}//
\endgl
\xe

@@

@@

@@
